Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2020-01-10 2016-Weak-FH-Bisim/WeakBisim.tex
dur dur le WOA
figures

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium.  
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectMedium} nodes are involved in the synchronization. More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time. And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.

@@

@@

\end{definition}
Rule $\WTUn$ states that it is always possible to do a null $\tau$ transition, where the state is unchanged and the holes perform no action. Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition. The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after a weak open transition. This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition. Their value thus depend of the initial state but also of the effect (as a substitution $\Post_1$) of the first weak open transition. In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$. Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition	.

>>>>

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium.  
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectBuffer}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization. More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time. And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.

@@

\begin{figure}[ht]
   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecOpen}}
   \caption{Specification OA}
   \label{SimpleProtCounter:SpecOA}
\end{figure}

@@

\end{definition}
Rule $\WTUn$ states that it is always possible to do a null $\tau$ transition, where the state is unchanged and the holes perform no action. Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition. The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after a weak open transition. This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition. Their value thus depend of the initial state but also of the effect (as a substitution $\Post_1$) of the first weak open transition. In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$. Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
